Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-30 WSSSPE3/report/wg_main_publishing_SW.tex
Fixed to do, and tweaked wording.

This group explored the value of executable papers (papers whose content includes
the code needed to produce their own results), and other forms of publishing which
include dynamic electronic content. Transitioning to this type of publication offers
possibilities of addressing, or partially addressing sustainability concerns 
such as reproducibility, transitive credit, and best practices.

@@

Reproducibility: Part of the purpose of these venues is to (at least partially)
address the reproducibility issue by making the paper itself recompute its own
results.

Software Credit (\S\ref{sec:software-credit}): Since these forms of publishing must make their sources explicit,
they should be easier to trace even if appropriately worded credit for software
is not provided. In addition, these notebooks make it possible to provide/define
additional metadata to make the tracing of credit clearer. In addition, attributions
could be added to citations to identify whether a paper extends a result, verifies it,
contradicts it, etc.

Best Practices: Because an executable paper showcases the code, and the code itself
is subject to the review process, authors are more likely to pay attention to coding
practices. In addition, because the paper must explain what the code does, better
documentation is likely to be achieved.

>>>>

This group explored the value of executable papers (papers whose content
includes the code needed to produce their own results), and other forms of
publishing which include dynamic electronic content. Transitioning to this type
of publication offers possibilities of addressing, or partially addressing
sustainability concerns such as reproducibility, software credit, and best
practices.

@@

\textbf{Reproducibility}: Part of the purpose of these executable paper venues
is to (at least partially) address the reproducibility issue by making the
paper itself recompute its own results.

\textbf{Software Credit (\S\ref{sec:software-credit})}: Since these forms of
publishing must make their sources explicit in order to execute, they should be
easier to trace even if appropriately worded credit for software is not
provided. In addition, these notebooks make it possible to provide/define
additional metadata to make the tracing of credit clearer. Finally,
attributions could be added to citations to identify whether a paper extends a
result, verifies it, contradicts it, etc.

\textbf{Best Practices (\S\ref{sec:best-practices})}: Because an executable paper
showcases the code, and the code itself is subject to the review process,
authors are more likely to pay attention to coding practices. In addition,
because the paper must explain what the code does, better documentation is
likely to be achieved.
